Parameterized convection, stratiform clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-29 resolution.tex
edits

The stratiform scheme becomes more active with resolution, compensating for the reduction in activity of the ZM scheme with resolution, particularly as it relates to the Intertropical Convergence Zone (ITCZ). Energetically, it is expected that stratiform precipitation rates increase with resolution to compensate for the reduction in convection from the ZM scheme in order to balance radiative cooling. But this argument requires one to assume the increase in stratiform precipitation is responding to a reduction in ZM activity, whereas this study indicates the reverse, that the ZM scheme is responding to increases in subsidence with resolution, driven by greater ascent associated with stratiform cloud formation. The authors instead sought to understand the increase in stratiform precipitation with resolution at the process level. It is shown that resolved upward moisture fluxes are highly correlated with stratiform precipitation rates, and that there is an increase in both upward moisture fluxes and stratiform precipitation with resolution. Through decomposing the stratiform precipitation in the ITCZ region into the components of the moisture flux, it is shown that larger magnitude vertical velocities are associated with larger stratiform precipitation rates, and these large precipitation rates increasingly contribute to the increase in climatological stratiform precipitation rate with resolution.

>>>>

The stratiform scheme becomes more active with resolution, compensating for the reduction in activity of the ZM scheme with resolution, particularly as it relates to the Intertropical Convergence Zone (ITCZ). Energetically, it may expected that stratiform precipitation rates increase with resolution to compensate for the reduction in convection from the ZM scheme in order to balance radiative cooling. But this argument requires one to assume the increase in stratiform precipitation is responding to a reduction in ZM activity, whereas this study indicates the reverse, that the ZM scheme is responding to increases in subsidence with resolution, driven by greater ascent from stratiform cloud formation. The authors instead sought to understand the increase in stratiform precipitation with resolution at the process level. It is shown that resolved upward moisture fluxes are highly correlated with stratiform precipitation rates, and that there is an increase in both upward moisture fluxes and stratiform precipitation with resolution. Through decomposing the stratiform precipitation in the ITCZ region into the components of the moisture flux, it is shown that larger magnitude vertical velocities are associated with larger stratiform precipitation rates, and these large precipitation rates increasingly contribute to the increase in climatological stratiform precipitation rate with resolution.
